---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VARim

<!-- badges: start -->
<!-- badges: end -->

VARim is a multivariate time series imputation method based on Vector Autoregression
(VAR) model. This imputation method was proposed by [Bashir and Wei (2018)](https://www.sciencedirect.com/science/article/abs/pii/S0925231217315515).
The package also includes improved methods that can be used on data with seasonality
and non-stationary data. An evaluation of this package, specifically for weather
data, can be accessed [here](https://ojs3.unpatti.ac.id/index.php/barekeng/article/view/6494).

## Installation

You can install the development version of VARim like so:

``` r
# install.packages("devtools")
library(devtools)
install_github("edyrizalmuh/VARim")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(VARim)
miss_data = omit(daily_weather, seed = 1, num_miss = 200)
colSums(is.na(miss_data)) # NA before imputation
imp_data = VARim(miss_data, init_method = "na_ma")
colSums(is.na(imp_data$imputed_data)) # NA after imputation
```
